The Noisy Work of Uncertainty Visualisation Research: A Review

### 2024-08-19 paper.qmd
replaced DT with flextable. Still have formatting issues. I'll deal with them later

# load Libraries
library(tidyverse)
library(biscale)
library(RColorBrewer)
library(scales)
library(sf)
library(ggrepel)
library(urbnmapr)
library(gt)
```

@@

@fig-data shows the first six rows of our example data, along with the geographical boundaries of our data set.  The temperature variable was generated using a quadratic spatial trend, that is $Temperature = 28-SLongitude^2 + SLatitude^2$ where the $SLongitide$ and $SLatitude$ are the scaled (to standard normal) longitude and latitude of the county's centroid. The high and low cases for the sampling variance are randomly sampled from a uniform distribution. The low standard errors are drawn from a $U_{[0,1]}$ distribution, while the high standard error cases are drawn from a a $U_{[1,2]}$ distribution. This is the data we will be using in our spatial uncertaity examples for the rest of the paper.

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-data
#| layout-nrow: 1
#| fig-cap: "The"
#| cap-location: "bottom"

@@

# Make nice table
example_table <- my_map_data |>
  mutate(variance = sqrt(variance)) |>
  select(c(count_id, county_name, temp, variance_class, variance)) |>
  as_tibble()|>
  pivot_wider(id_cols=c(count_id, county_name, temp,), 
              names_from = variance_class, 
              values_from = variance) |>
  head()|>
  gt() |>
   tab_header(
    title = "Average Daily High Temperatures of Iowa Counties",
    subtitle = "Psudo-data with high standard error and low standard error cases") |>
  tab_spanner(
    label = "Standard Error",
    columns = c(highvar, lowvar)
  ) |>
  cols_label( 
    count_id = "ID", 
    county_name  = "County",
    temp = "Temperature (°C)",
    highvar = "High",
    lowvar = "Low"
    ) |>
  fmt_number(columns = c(temp, highvar, lowvar)) |>
  data_color(
    columns = temp,
    method = "numeric",
    palette = "Oranges",
    domain = c(21, 29)
  ) |>
  data_color(
    columns = c(highvar, lowvar),
    method = "numeric",
    palette = "Greens",
    domain = c(0, 3)
  ) |>
  as_latex()

>>>>

# load Libraries
library(tidyverse)
library(biscale)
library(RColorBrewer)
library(scales)
library(sf)
library(ggrepel)
library(urbnmapr)
library(flextable)
```

@@

@fig-data shows the first six rows of our example data, along with the geographical boundaries of our data set. The temperature variable was generated using a quadratic spatial trend, that is $Temperature = 28-SLongitude^2 + SLatitude^2$ where the $SLongitide$ and $SLatitude$ are the scaled (to standard normal) longitude and latitude of the county's centroid. The high and low cases for the sampling variance are randomly sampled from a uniform distribution. The low standard errors are drawn from a $U_{[0,1]}$ distribution, while the high standard error cases are drawn from a a $U_{[1,2]}$ distribution. As we are dealing with an average, the sampling distribution would be normally distributed, so each county temperature estimate is assumed to come from a $N(Temp_i, SE_{case,i})$. This is the data we will be using in our spatial uncertainty examples for the rest of the paper.

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-data
#| fig-cap: "The"
#| cap-location: "bottom"

@@

# Make nice example table
example_table <- my_map_data |>
  mutate(variance = sqrt(variance)) |>
  select(c(count_id, county_name, temp, variance_class, variance)) |>
  as_tibble()|>
  pivot_wider(id_cols=c(count_id, county_name, temp,), 
              names_from = variance_class, 
              values_from = variance) |>
  head()|>
  flextable() |>
  set_caption(caption = "Average Daily High Temperatures of Iowa Counties") |>
  add_header_row(colwidths = c(3, 2),
                 values = c("", "Standard Error")) |>
  colformat_double(digits = 2) |>
  set_header_labels(count_id = "ID", 
                    county_name  = "County",
                    temp = "Temperature (°C)",
                    highvar = "High",
                    lowvar = "Low") |>
  theme_vanilla() |>
  vline(i=c(1,2), j=3, part="header")|>
  align(align = "left", part = "all") |>
  bg(j = "temp",
    bg = col_numeric(palette = brewer.pal(8, name = "Oranges"),
                     domain = c(21, 30)),
    part = "body"
  ) |>
  bg(j = c("highvar", "lowvar"),
    bg = col_numeric(palette = brewer.pal(8, name = "Greens"),
                     domain = c(0, 3)),
    part = "body"
  )
